---
title: "2019 Hoophouse Data"
author: "SS"
date: "10/2/2019"
output:
  html_document: default
  word_document: default
---

```{r include=FALSE}
library(betareg)
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(lme4)
library(car)
library(emmeans)
library(multcompView)
library(agricolae)
library(nlme)
library(lmerTest)
library(multcomp)
library(bestNormalize)
library(glmmTMB)
library(ggpubr)
library(nortest)
library(zoo)
library(predictmeans)
library(agricolae)
```

```{r include=FALSE}
Data <- read.csv("injury.csv", header=T)
str(Data)
dim(Data)
Data$Trt= as.factor(Data$Trt)
str(Data)
```

#Plotting Raw Data

SB25a - Run 1 or R1; SB25b - Run 2 or R2

Treatments:1 & 2 - Nontreated Check; 3 & 4 - Xtendimax; 5 & 6 - Xtendimax + Roundup Powermax; 7 & 8 - Status; 9 & 10 - Status + Roundup Powermax; 11 & 12 - Enlist One; 13 & 14 - Enlist DUO

Figure Legend: Maroon = Nontreated Check; Navy = No GLY; Grey = GLY

```{r}
#Filter to plot, rough plot of injury over distance
data = Data %>%
  filter(Trial=="SB25b", Rating=="28 DAT", Plot=="301")
plot(data$Distance, data$injury)

#ggplot of injury over distance for filtered "data" above
ggplot(data, aes(x = Distance, y=injury, group=Distance, fill=injury)) +
  geom_point() + 
  theme_bw() + theme(plot.title =  element_text(size=30, color="black", face="bold"),
                     axis.title.y = element_text(size=18, color="black", face="bold"),
                     axis.title.x = element_text(size=18, color="black"), 
                     legend.position="none",
                     axis.text.x = element_text(size=15, color="black"),
                     axis.text.y = element_text(size=15, color="black"), 
                     strip.text.y = element_text(size=25, color="black", face="bold"),
                     panel.background = element_rect(fill="white"),
                     panel.grid.major=element_line(color="white"),
                     panel.grid.minor=element_line(color="white")) +
  labs(y="Injury (%)", x="Distance from Plot Center (m)") +
  scale_x_continuous(breaks=c(0,0.3,0.6,0.9,1.2,1.5,1.8,2.1,2.4,2.7, 3)) +
  scale_y_continuous(limits=c(0, 25)) +
  ggsave("Sup1.tiff", units="in", width=8, height=6, dpi=600)
```

#Injury Figures for posters/supplemental for paper(on raw injury data)

SB25a Early, 28 DAT
```{r}
data1 = Data%>%
  filter(Trial=="SB25a", App=="Early", Rating=="28 DAT")
data1 <- subset(data1, herb!="none")
table(data1$herb)
table(droplevels(data1)$herb)
str(data1)

ggplot(data1, aes(x = Distance, y=injury, group=Distance, fill=injury)) +
  geom_boxplot(fill="mistyrose4") + geom_jitter(alpha=0.2, color="red4") + 
  facet_grid(herb ~ .) + 
  ggtitle("Early application, experiment 1") +
  theme_bw() + theme(plot.title =  element_text(size=25, hjust=0.5, color="black", face="bold"),
                     axis.title.y = element_text(size=25, color="black", face="bold"),
                     axis.title.x = element_text(size=25, color="black"), 
                     legend.position="none",
                     axis.text.x = element_text(size=15, color="black"),
                     axis.text.y = element_text(size=15, color="black"), 
                     strip.text.y = element_text(size=25, color="black", face="bold"),
                     panel.background = element_rect(fill="white"),
                     panel.grid.major=element_line(color="white"),
                     panel.grid.minor=element_line(color="white")) +
  labs(y="Injury (%)", x="Distance from plot center (m)") +
  scale_x_continuous(breaks=c(0,0.3,0.6,0.9,1.2,1.5,1.8,2.1,2.4,2.7, 3)) +
  scale_y_continuous(limits=c(0, 30)) +
  ggsave("R1Early.tiff", units="in", width=10, height=8, dpi=600)
```

SB25b Early, 28 DAT
```{r}
data2 = Data%>%
  filter(Trial=="SB25b", App=="Early", Rating=="28 DAT")
data2 <- subset(data2, herb!="none")
table(data2$herb)
table(droplevels(data2)$herb)
str(data2)

ggplot(data2, aes(x = Distance, y=injury, group=Distance, fill=injury)) +
  geom_boxplot(fill="mistyrose4") + geom_jitter(alpha=0.2, color="red4") + 
  facet_grid(herb ~ .) + 
  ggtitle("Early application, experiment 2") +
  theme_bw() + theme(plot.title =  element_text(size=25, hjust=0.5, color="black", face="bold"),
                     axis.title.y = element_text(size=25, color="black", face="bold"),
                     axis.title.x = element_text(size=25, color="black"), 
                     legend.position="none",
                     axis.text.x = element_text(size=15, color="black"),
                     axis.text.y = element_text(size=15, color="black"), 
                     strip.text.y = element_text(size=25, color="black", face="bold"),
                     panel.background = element_rect(fill="white"),
                     panel.grid.major=element_line(color="white"),
                     panel.grid.minor=element_line(color="white")) +
  labs(y="Injury (%)", x="Distance from plot center (m)") +
  scale_x_continuous(breaks=c(0,0.3,0.6,0.9,1.2,1.5,1.8,2.1,2.4,2.7, 3)) +
  scale_y_continuous(limits=c(0, 30)) +
  ggsave("R2Early.tiff", units="in", width=10, height=8, dpi=600)
```

SB25a Late, 28 DAT
```{r}
data3 = Data%>%
  filter(Trial=="SB25a", App=="Late", Rating=="28 DAT")
data3 <- subset(data3, herb!="none")
table(data3$herb)
table(droplevels(data3)$herb)
str(data3)

ggplot(data3, aes(x = Distance, y=injury, group=Distance, fill=injury)) +
  geom_boxplot(fill="mistyrose4") + geom_jitter(alpha=0.2, color="red4") + 
  facet_grid(herb ~ .) + 
  ggtitle("Late application, experiment 1") +
  theme_bw() + theme(plot.title =  element_text(size=25, hjust=0.5, color="black", face="bold"),
                     axis.title.y = element_text(size=25, color="black", face="bold"),
                     axis.title.x = element_text(size=25, color="black"), 
                     legend.position="none",
                     axis.text.x = element_text(size=15, color="black"),
                     axis.text.y = element_text(size=15, color="black"), 
                     strip.text.y = element_text(size=25, color="black", face="bold"),
                     panel.background = element_rect(fill="white"),
                     panel.grid.major=element_line(color="white"),
                     panel.grid.minor=element_line(color="white")) +
  labs(y="Injury (%)", x="Distance from plot center (m)")  +
  scale_x_continuous(breaks=c(0,0.3,0.6,0.9,1.2,1.5,1.8,2.1,2.4,2.7, 3)) +
  scale_y_continuous(limits=c(0, 30)) +
  ggsave("R1Late.tiff", units="in", width=10, height=8, dpi=600)
```

SB25b Late, 28 DAT
```{r}
data4 = Data%>%
  filter(Trial=="SB25b", App=="Late", Rating=="28 DAT")
data4 <- subset(data4, herb!="none")
table(data4$herb)
table(droplevels(data4)$herb)
str(data4)

ggplot(data4, aes(x = Distance, y=injury, group=Distance, fill=injury)) +
  geom_boxplot(fill="mistyrose4") + geom_jitter(alpha=0.2, color="red4") + 
  facet_grid(herb ~ .) + 
  ggtitle("Late application, experiment 2") +
  theme_bw() + theme(plot.title =  element_text(size=25, hjust=0.5, color="black", face="bold"),
                     axis.title.y = element_text(size=25, color="black", face="bold"),
                     axis.title.x = element_text(size=25, color="black"), 
                     legend.position="none",
                     axis.text.x = element_text(size=15, color="black"),
                     axis.text.y = element_text(size=15, color="black"), 
                     strip.text.y = element_text(size=25, color="black", face="bold"),
                     panel.background = element_rect(fill="white"),
                     panel.grid.major=element_line(color="white"),
                     panel.grid.minor=element_line(color="white")) +
  labs(y="Injury (%)", x="Distance from plot center (m)") +
  scale_x_continuous(breaks=c(0,0.3,0.6,0.9,1.2,1.5,1.8,2.1,2.4,2.7, 3)) +
  scale_y_continuous(limits=c(0, 30)) +
  ggsave("R2Late.tiff", units="in", width=10, height=8, dpi=600)
```

#Area Under Disease Progress Stairs Calculations

Using agricolae's "audps" function for calculation.

```{r AUDPS calculations}
#Filter data to plot level
data = Data %>%
  filter(Trial=="SB25b", Rating=="28 DAT", Plot=="312")
#check to make sure data looks right before calculation
plot(data$Distance, data$injury)
#Calculation below. Specify "absolute" or "relative" for type=. Transcribe value in datafile, repeat process for all other plots.
audps(data$injury, data$Distance, type="absolute")
```


#AUDPS analysis

```{r AUDPS analysis}
#upload new data file
Data2 <- read.csv("audps.csv", header=T)
str(Data2)
Data2$Trt= as.factor(Data2$Trt)
Data2$run=as.factor(Data2$run)
Data2$rep=as.factor(Data2$rep)
str(Data2)

mean <-round(tapply(Data2$audps,Data2$Trt.Des, mean),2)
mean
#went back into datafile and mean for Check was 1.75 so that number was subtracted from each plot and reset to 0 for anything <0, renamed variable AUDPS and imported data file again

Data2 <- read.csv("audps.csv", header=T)
str(Data2)
Data2$Trt= as.factor(Data2$Trt)
Data2$run=as.factor(Data2$run)
Data2$rep=as.factor(Data2$rep)
str(Data2)
```

```{r Model assumptions}
Data2 <- subset(Data2, Trt.Des!="Check")
table(Data2$Trt.Des)
table(droplevels(Data2)$Trt.Des)
str(Data2)
Data2 <- subset(Data2, herb!="none")
table(Data2$herb)
table(droplevels(Data2)$herb)
str(Data2)
Data2 <- subset(Data2, gly!="none")
table(Data2$gly)
table(droplevels(Data2)$gly)
str(Data2)
Data2$app

Data2 <- Data2 %>%   
  mutate(tAUDPS = sqrt(AUDPS))

#First, run the model
model=lmer(sqrt(AUDPS) ~ run*app*herb*gly + (1|run:rep), data=Data2)

#Assess assumptions
#normality - statistical tests and graphical checks
residuals = resid(model)
shapiro.test(residuals)
pearson.test(residuals)
qqnorm(residuals); qqline(residuals, col=2)
hist(residuals,freq=F, xlab="Residuals", ylab="Frequency", main="")
#equal variance - statistical tests and graphical checks
leveneTest(tAUDPS ~ herb*gly, data=Data2)
plot(model)

#then, proceed with analysis
summary(model)
anova(model, test.statistic = "F")

#model2=lmer(sqrt(AUDPS) ~ run*app*herb + (1|run:rep), data=Data2)
#summary(model2)
#anova(model2, test.statistic = "F")
```

```{r}
lsm <- emmeans(model, ~ herb | app*run,  type="response", adjust="tukey", contr="pairwise")
lsm

cld <- CLD(lsm, adjust="tukey", reversed=TRUE, Letters= letters)
cld
```


#AUIDS figures by herbicide for specified/filtered application timing and run combinations for posters

```{r}
cld1 = cld%>%
  filter(app=="early", run=="1")

ggplot(cld1, aes(x = herb, y=response, label=.group, fill=herb)) +
  geom_bar(stat="identity", width = 0.6, color="black") + 
  geom_errorbar(aes(ymin  =  lower.CL, ymax  =  upper.CL), width =  0.1, size  =  0.7) +
  ggtitle("Early Application, Run 1") +
  scale_fill_manual(values=c("#646569", "#adadad", "#c5050c"), name="", 
                    labels=c("2,4-D", "NA+DIF", "DGA+VG")) +
  theme_bw() + theme(plot.title =  element_text(size=25, color="black", face="bold"),
                     axis.title.y = element_text(size=20, color="black", face="bold"),
                     #axis.title.x = element_text(size=25, color="black", face="bold"),
                     legend.position="bottom", legend.direction = "horizontal", 
                     legend.box = "horizontal", 
                     legend.text = element_text(color="black", size = 20), 
                     legend.title = element_blank(),
                     axis.text.x = element_blank(),
                     axis.title.x = element_blank(),
                     axis.text.y = element_text(size=15, color="black"), 
                     strip.text.y = element_text(size=25, color="black", face="bold"),
                     panel.background = element_rect(fill="white"),
                     panel.grid.major=element_line(color="white"),
                     panel.grid.minor=element_line(color="white")) +
  labs(y="AUIDS", x="") +
  scale_y_continuous(limits=c(0,50)) +
  ggsave("R1EarlyV2.tiff", units="in", width=10, height=8, dpi=600)
```

```{r}
cld2 = cld%>%
  filter(app=="early", run=="2")

ggplot(cld2, aes(x = herb, y=response, label=.group, fill=herb)) +
  geom_bar(stat="identity", width = 0.6, color="black") + 
  geom_errorbar(aes(ymin  =  lower.CL, ymax  =  upper.CL), width =  0.1, size  =  0.7) +
  ggtitle("Early Application, Run 2") +
  scale_fill_manual(values=c("#646569", "#adadad", "#c5050c"), name="", 
                    labels=c("2,4-D", "NA+DIF", "DGA+VG")) +
  theme_bw() + theme(plot.title =  element_text(size=25, color="black", face="bold"),
                     axis.title.y = element_text(size=20, color="black", face="bold"),
                     #axis.title.x = element_text(size=25, color="black", face="bold"),
                     legend.position="bottom", legend.direction = "horizontal", 
                     legend.box = "horizontal", 
                     legend.text = element_text(color="black", size = 20), 
                     legend.title = element_blank(),
                     axis.text.x = element_blank(),
                     axis.title.x = element_blank(),
                     axis.text.y = element_text(size=15, color="black"), 
                     strip.text.y = element_text(size=25, color="black", face="bold"),
                     panel.background = element_rect(fill="white"),
                     panel.grid.major=element_line(color="white"),
                     panel.grid.minor=element_line(color="white")) +
  labs(y="AUIDS", x="") +
  scale_y_continuous(breaks=c(0,10,20,30,40,50)) +
  ggsave("R2EarlyV2.tiff", units="in", width=10, height=8, dpi=600)
```

```{r}
cld3 = cld%>%
  filter(app=="late", run=="1")

ggplot(cld3, aes(x = herb, y=response, label=.group, fill=herb)) +
  geom_bar(stat="identity", width = 0.6, color="black") + 
  geom_errorbar(aes(ymin  =  lower.CL, ymax  =  upper.CL), width =  0.1, size  =  0.7) +
  ggtitle("Late Application, Run 1") +
  scale_fill_manual(values=c("#646569", "#adadad", "#c5050c"), name="", 
                    labels=c("2,4-D", "NA+DIF", "DGA+VG")) +
  theme_bw() + theme(plot.title =  element_text(size=25, color="black", face="bold"),
                     axis.title.y = element_text(size=20, color="black", face="bold"),
                     #axis.title.x = element_text(size=25, color="black", face="bold"),
                     legend.position="bottom", legend.direction = "horizontal", 
                     legend.box = "horizontal", 
                     legend.text = element_text(color="black", size = 20), 
                     legend.title = element_blank(),
                     axis.text.x = element_blank(),
                     axis.title.x = element_blank(),
                     axis.text.y = element_text(size=15, color="black"), 
                     strip.text.y = element_text(size=25, color="black", face="bold"),
                     panel.background = element_rect(fill="white"),
                     panel.grid.major=element_line(color="white"),
                     panel.grid.minor=element_line(color="white")) +
  labs(y="AUIDS", x="") +
  scale_y_continuous(limits=c(0,50)) +
  ggsave("R1LateV2.tiff", units="in", width=10, height=8, dpi=600)
```

```{r}
cld4 = cld%>%
  filter(app=="late", run=="2")

ggplot(cld4, aes(x = herb, y=response, label=.group, fill=herb)) +
  geom_bar(stat="identity", width = 0.6, color="black") + 
  geom_errorbar(aes(ymin  =  lower.CL, ymax  =  upper.CL), width =  0.1, size  =  0.7) +
  ggtitle("Late Application, Run 2") +
  scale_fill_manual(values=c("#646569", "#adadad", "#c5050c"), name="", 
                    labels=c("2,4-D", "NA+DIF", "DGA+VG")) +
  theme_bw() + theme(plot.title =  element_text(size=25, color="black", face="bold"),
                     axis.title.y = element_text(size=20, color="black", face="bold"),
                     #axis.title.x = element_text(size=25, color="black", face="bold"),
                     legend.position="bottom", legend.direction = "horizontal", 
                     legend.box = "horizontal", 
                     legend.text = element_text(color="black", size = 20), 
                     legend.title = element_blank(),
                     axis.text.x = element_blank(),
                     axis.title.x = element_blank(),
                     axis.text.y = element_text(size=15, color="black"), 
                     strip.text.y = element_text(size=25, color="black", face="bold"),
                     panel.background = element_rect(fill="white"),
                     panel.grid.major=element_line(color="white"),
                     panel.grid.minor=element_line(color="white")) +
  labs(y="AUIDS", x="") +
  scale_y_continuous(breaks=c(0,10,20,30,40,50)) +
  ggsave("R2LateV2.tiff", units="in", width=10, height=8, dpi=600)
```

